The noise-marginalized optimal statistic: A robust hybrid frequentist-Bayesian statistic for the stochastic gravitational-wave background in pulsar timing arrays

### 2018-05-30 manuscript/manuscript.tex
final round of edits

\begin{abstract}
Observations have revealed that nearly all galaxies 
contain supermassive black holes (SMBHs) at their centers. 
When galaxies merge, these SMBHs form SMBH binaries (SMBHBs), 
which emit low-frequency gravitational waves (GWs). 
The incoherent superposition of these sources produce a stochastic GW background (GWB) 
that can be observed by pulsar timing arrays (PTAs). 
The optimal statistic is a frequentist estimator of the amplitude of the GWB 
that specifically looks for the spatial correlations between pulsars induced by the GWB. 
In this paper, we introduce an improved method for computing the optimal statistic 
that marginalizes over the red noise in individual pulsars. 
We use simulations to demonstrate that this method 
more accurately determines the strength of the GWB, 
and we use the noise-marginalized optimal statistic 
to compare the significance of monopole, dipole, and Hellings-Downs (HD) spatial correlations 
and perform sky scrambles.
\end{abstract}

@@

Long-wavelength gravitational waves (GWs) with frequencies of 
$10^{-9} - 10^{-7} \; \mathrm{Hz}$ can be observed with pulsar timing arrays (PTAs) 
composed of millisecond pulsars (MSPs) \cite{hd1983,fb1990}. 
The dominant astrophysical source in this frequency range is the isotropic stochastic 
gravitational wave background (GWB) 
made up of the incoherent superposition of GWs from inspiraling 
supermassive black hole binaries (SMBHBs) 
\citep{1995ApJ...446..543R, 2003ApJ...583..616J, 2003ApJ...590..691W}. 
By monitoring the periodic emission from these pulsars using radio telescopes, 
we can probe the dynamics of the spacetime through which the pulses travel. 
This is done by searching for correlations in the pulsar timing residuals, 
which measure the difference between the expected and observed pulse times of arrival. 
Current upper limits on the stochastic background from PTAs are approaching 
theoretical predictions for the GWB \citep{PPTA2013,EPTA2015,abb+17b}

PTAs primarily use Bayesian data analysis to compare the inferred probabilities 
of various models for the residuals, 
including one where they contain evidence of the GWB 
\citep{vlm+2009,lah+2013}. 
%Bayesian inference is a powerful technique because it allows us to compare arbitrarily complicated models. 
Bayesian inference is a powerful tool because 
it properly accounts for degeneracies between parameters 
and incorporate all sources of uncertainty into the analysis. 
However, running a full Bayesian analysis is computationally intensive, 
particularly when searching for evidence of Hellings-Downs (HD) spatial correlations --
the ``smoking gun'' of the GWB.

The significance of the GWB can also be assessed using the 
optimal statistic, a frequentist estimator for the GWB amplitude \citep{abc+2009,demorest+2013,ccs+2015}. 
%It is an important complement to Bayesian detection techniques 
%because it provides an independent detection procedure, 
%and it is significantly faster to compute. 
%In particular, different spatial correlations can be tested with the optimal statistic 
%in less than a second, 
%whereas a Bayesian analysis with spatial correlations requires 
%several weeks to run on a supercomputing cluster.
Not only does it provide an independent detection procedure, complementing a more robust Bayesian analysis, but it requires significantly less time to compute. In particular, the optimal statistic produces results for various spatial correlation functions within seconds; a full Bayesian analysis including correlations has to run for many weeks on a supercomputing cluster.

However, when pulsars have significant red noise, 
the optimal statistic gives biased results 
due to the strong covariance 
between the individual red noise parameters and the GWB amplitude. 
Many individual pulsars show evidence for red noise \citep{lam+2017,abb+17}, 
and uncertainty in the position of the Solar System barycenter (SSB) leads to 
a common red process in all pulsars \citep{abb+17b}. 
%In this paper, we present a technique for improving the accuracy of the optimal statistic 
%by marginalizing the optimal statistic over the individual red noise parameters 
%using the posterior distributions from a full Bayesian analysis. 
%This hybrid approach produces a more accurate 
%estimate of \Agw\ and its uncertainty. 
Here we present a technique for improving the accuracy of the optimal statistic by including an additional step: 
marginalizing over the individual pulsar red noise parameters 
using the posterior distributions from a full Bayesian analysis of all the pulsars. 
This hybrid approach produces a more precise estimate of the GWB amplitude \Agw\ 
and its uncertainty, while requiring only a few minutes more than the more traditional method of computation. 
%This method is more computationally intensive than previous methods 
%for computing the optimal statistic, but still requires only minutes. 
%Furthermore, the same Bayesian analysis drawn upon by the noise marginalization 
%can be used to compute the optimal statistic with any choice of the ORF, 
%allowing additional spatial correlations to be tested very quickly.
Furthermore, the same Bayesian analysis drawn upon by the noise marginalization 
can be used to compute the optimal statistic for any choice of spatial correlations 
simply by changing the overlap-reduction function (ORF). 
For example, clock errors lead to a common red signal with monopole spatial correlations \citep{hcm+2012}, 
while uncertainty in the SSB produces dipole spatial correlations \citep{chm+2010}. 
This technique is used to perform the frequentist searches 
for common red signals with HD, 
monopole, and dipole spatial correlations 
in the NANOGrav 11-year data set \citep{abb+17b}.

@@

The optimal statistic is constructed from the autocovariance and cross-covariance matrices 
$C_a$ and $S_{ab}$, 
\begin{eqnarray}
	C_a &=& \left\langle \res_a \res_a^T \right\rangle \,, \\
	S_{ab} &=& \left. \left\langle \res_a \res_b^T \right\rangle \right|_{a \neq b} \,,
\end{eqnarray}
where $\res_a$ is a vector of the residuals of the $a$th pulsar in the PTA. 
For the GWB with power spectral density (PSD) $P_\mathrm{gw}(f)$ 
and overlap reduction function (ORF) $\Gamma_{ab}$, 
the cross-covariance matrices are
\begin{equation}
	S_{ab} = F_a \, \phi_{ab}^\mathrm{gw} \, F_b^T \,,
\end{equation}
where
\begin{equation}
	\phi_{ab}^\mathrm{gw} = \Gamma_{ab} \, P_\mathrm{gw}(f) \,,
	\label{eq:phi_gw}
\end{equation}
and the ORF is the HD curve \citep{hd1983}, 
\begin{eqnarray}
	\Gamma_{ab} &=& \frac{1}{2} \left[ 1 - \frac{1}{2} \left( \frac{1-\cos\theta_{ab}}{2} \right) \right. \nonumber \\
		&& \left. + 3 \left( \frac{1-\cos\theta_{ab}}{2} \right) \ln \left( \frac{1-\cos\theta_{ab}}{2} \right) \right]  \,,
\end{eqnarray}
where $\theta_{ab}$ is the angle between the pulsars. 
We model the PSD of the GWB as a power law:
\begin{equation}
	P_\mathrm{gw}(f) = \frac{\Agw^2}{12\pi^2} \left( \frac{f}{f_\mathrm{yr}} \right)^{-\gamma} \,,
\end{equation}
where $\gamma = 13/3$ assuming SMBHBs evolve solely due to GW emission and $f_\mathrm{yr} \equiv 1/(1\,\mathrm{yr})$. 
The optimal statistic $\hat{A}^2$ is given by
\begin{equation}
	\hat{A}^2 = \frac{\sum_{ab} \res_a^T {C_a^{-1} \tilde{S}_{ab} C_b^{-1} \res_b}}{\sum_{ab} \Tr \left( C_a^{-1} \tilde{S}_{ab} C_b^{-1} \tilde{S}_{ba} \right) } \,,
\end{equation}
where $\tilde{S}_{ab}$ is the amplitude-independent cross-correlation matrix,
\begin{equation}
	\Agw^2 \tilde{S}_{ab} = S_{ab} \,.
\end{equation}
This definition of the optimal statistic ensures that  
$\langle \hat{A}^2 \rangle = \Agw^2$. 
If $\Agw=0$, the variance of the optimal statistic is
\begin{equation}
	\sigma_0 = \left[ \sum_{ab} \Tr \left( C_a^{-1} \tilde{S}_{ab} C_b^{-1} \tilde{S}_{ba} \right) \right]^{-1/2} \,.
\end{equation}
For a measured value of $\hat{A}^2$, 
the significance of $\hat{A}^2 \neq 0$ is given by the signal-to-noise ratio (SNR) 
\begin{equation}
	\rho = \frac{\sum_{ab} \res_a^T {C_a^{-1} \tilde{S}_{ab} C_b^{-1} \res_b}}{ \left[ \sum_{ab} \Tr \left( C_a^{-1} \tilde{S}_{ab} C_b^{-1} \tilde{S}_{ba} \right) \right]^{1/2}} \,.
\end{equation}

When constructing the residuals $\res_a$, 
we typically fix the red noise parameters to the values that 
maximize the single-pulsar likelihood. 
However, this leads to a bias in the optimal statistic 
because the individual red noise and common red noise parameters 
are highly covariant, 
with the optimal statistic systematically lower than the true value of $\Agw^2$. 
In this section, we compare three techniques for computing the optimal statistic. 
First, we fix the individual pulsars' red noise parameters to the 
maximum-likelihood values from individual Bayesian pulsar noise analyses. 
Second, we fix the pulsars' red noise parameters to the 
values that jointly maximize the likelihood for a Bayesian analysis 
of all of the pulsars in our PTA 
that searches over the pulsars' red noise parameters and 
a common red process. 
For the noise-marginalized method, we draw values of the pulsars' 
red noise parameters from the posteriors generated by the common Bayesian analysis.

We use these methods to compute the optimal statistic 
for simulated ``NANOGrav-like'' data sets 
consisting of 18 MSPs with observation times up to 11 years 
and sky positions matching the 18 longest-observed pulsars in the 
NANOGrav 11-year data set \citep{abb+17}. 
We include white noise for all pulsars, plus 
red noise parametrized as a power law, 
\begin{equation}
	P_a(f) = \frac{A_\mathrm{red}^2}{12\pi^2} \left( \frac{f}{f_\mathrm{yr}} \right)^{-\gamma} \,,
\end{equation}
for those pulsars that show evidence of red noise 
(see Table~\ref{tab:sim} for more details).
We use the PTA data analysis package 
PAL2 %\footnote{\href{https://github.com/jellis18/PAL2}{https://github.com/jellis18/PAL2}} 
\citep{evh17a}
to perform the noise analyses and compute the optimal statistic.

@@

This overlap between the monopole, dipole, and HD ORFs also means that 
a common red process that does not have HD correlations  
may be confused for a GWB. Figure~\ref{fig:os_dipole} shows the results of 25 simulations 
containing a stochastic signal with dipole spatial correlations. 
Although a dipole signal has been injected, 
the HD ORF gives a mean SNR greater than 5 in 82\% of the simulations. 
However, both the monopole and HD ORFs give smaller values of 
the mean $\hat{A}^2$ and mean SNR compared to the dipole ORF. 
Furthermore, there are no simulations for which the mean SNR with HD ORF 
is greater than the mean SNR with dipole ORF. 
This demonstrates the importance of comparing the SNR from different spatial correlations 
when determining the type of spatial correlations present.
\begin{figure}[t]
	\includegraphics[width=0.9\columnwidth]{plots/optstat_dipole_A5e-15.pdf}
	\caption{Noise-marginalized mean optimal statistic and mean SNR for 25 simulated data sets 
			containing an injected stochastic signal with dipole spatial correlations and $A = 5\times10^{-15}$. 
			We compare the values of the optimal statistic and mean SNR 
			found using monopole (blue), dipole (orange), 
			and HD (green) spatial correlations. 
			The dashed vertical line indicates the injected value, $\hat{A}^2 = 2.5 \times 10^{-29}$.}
	\label{fig:os_dipole}
\end{figure}

@@

The significance of spatial correlations can also be tested with ``sky scrambles,'' 
where the ORF is altered in order to simulate changing the pulsars' positions \citep{cs2016,tlb+2017}. 
The scrambled ORFs are required to have small values of $\bar{M}$ 
with the true ORF and each other so that they form a nearly-orthogonal set. 
This ensures that the distribution of $\hat{A}^2$ computed using the scrambled ORFs 
forms the null hypothesis distribution. 
\citet{tlb+2017} showed how sky scrambles affect the Bayes' factor for simulated data sets. 
Here we perform a similar analysis using frequentist methods.

@@

\acknowledgments
We thank Joe Lazio, Andrea Lommen, Joe Romano, Xavier Siemens, and Jolien Creighton for useful discussions. 
This work was supported by NSF Physics Frontier Center Grant 1430284. 
%SRT was partially supported by appointment to the NASA Postdoctoral Program 
%at the Jet Propulsion Laboratory, which is administered by Oak Ridge Associated Universities 
%and the Universities Space Research Association through a contract with NASA. 
JAE was partially supported by NASA through Einstein Fellowship Grant PF4-150120. 
We are grateful for computational resources provided by the Leonard E Parker
Center for Gravitation, Cosmology and Astrophysics at the University of
Wisconsin-Milwaukee.

>>>>

\begin{abstract}
Observations have revealed that nearly all galaxies 
contain supermassive black holes (SMBHs) at their centers. 
When galaxies merge, these SMBHs form SMBH binaries (SMBHBs) 
that emit low-frequency gravitational waves (GWs). 
The incoherent superposition of these sources produce a stochastic GW background (GWB) 
that can be observed by pulsar timing arrays (PTAs). 
The optimal statistic is a frequentist estimator of the amplitude of the GWB 
that specifically looks for the spatial correlations between pulsars induced by the GWB. 
In this paper, we introduce an improved method for computing the optimal statistic 
that marginalizes over the red noise in individual pulsars. 
We use simulations to demonstrate that this method 
more accurately determines the strength of the GWB, 
and we use the noise-marginalized optimal statistic 
to compare the significance of monopole, dipole, and Hellings-Downs (HD) spatial correlations 
and perform sky scrambles.
\end{abstract}

@@

Long-wavelength gravitational waves (GWs) with frequencies of 
$10^{-9} - 10^{-7} \; \mathrm{Hz}$ can be observed with pulsar timing arrays (PTAs) 
composed of millisecond pulsars (MSPs) \cite{hd1983,fb1990}. 
The dominant astrophysical source in this frequency range is the isotropic stochastic 
gravitational wave background (GWB) 
made up of the incoherent superposition of GWs from inspiraling 
supermassive black hole binaries (SMBHBs) 
\citep{1995ApJ...446..543R, 2003ApJ...583..616J, 2003ApJ...590..691W}. 
By monitoring the periodic emission from these pulsars using radio telescopes, 
we can probe the dynamics of the spacetime through which the pulses travel. 
This is done by searching for correlations in the pulsar timing residuals, 
which measure the differences between the expected and observed pulse times of arrival. 
Current upper limits on the stochastic background from PTAs are approaching 
theoretical predictions for the GWB \citep{PPTA2013,EPTA2015,abb+17b}

PTAs primarily use Bayesian data analysis to compare the inferred probabilities 
of various models for the residuals, 
including one where they contain the GWB 
\citep{vlm+2009,lah+2013}. 
%Bayesian inference is a powerful technique because it allows us to compare arbitrarily complicated models. 
Bayesian inference is a powerful tool because 
it properly accounts for degeneracies between parameters 
and incorporates all sources of uncertainty into the analysis. 
However, running a full Bayesian analysis is computationally intensive, 
particularly when searching for evidence of Hellings-Downs (HD) spatial correlations --
the ``smoking gun'' of the GWB.

The significance of the GWB can also be assessed using the 
optimal statistic, a frequentist estimator for the GWB amplitude \citep{abc+2009,demorest+2013,ccs+2015}. 
%It is an important complement to Bayesian detection techniques 
%because it provides an independent detection procedure, 
%and it is significantly faster to compute. 
%In particular, different spatial correlations can be tested with the optimal statistic 
%in less than a second, 
%whereas a Bayesian analysis with spatial correlations requires 
%several weeks to run on a supercomputing cluster.
Not only does it provide an independent detection procedure, complementing a more robust Bayesian analysis, but it requires significantly less time to compute. In particular, the optimal statistic produces results for a given spatial correlation function within seconds; a full Bayesian analysis including correlations has to run for many weeks on a supercomputing cluster.

However, when pulsars have significant red noise 
the optimal statistic gives biased results 
due to the strong covariance 
between the individual red noise parameters and the GWB amplitude. 
Many individual pulsars show evidence for red noise \citep{lam+2017,abb+17}, 
and uncertainty in the position of the Solar System barycenter (SSB) leads to 
a common red process in all pulsars \citep{abb+17b}. 
%In this paper, we present a technique for improving the accuracy of the optimal statistic 
%by marginalizing the optimal statistic over the individual red noise parameters 
%using the posterior distributions from a full Bayesian analysis. 
%This hybrid approach produces a more accurate 
%estimate of \Agw\ and its uncertainty. 
Here we present a technique for improving the accuracy of the optimal statistic by including an additional step: 
marginalizing over the individual pulsars' red noise parameters 
using the posterior distributions from a full Bayesian analysis of all the pulsars. 
This hybrid approach produces a more precise estimate of the GWB amplitude \Agw\ 
and its uncertainty, while requiring only a few minutes more than the more traditional method of computation. 
%This method is more computationally intensive than previous methods 
%for computing the optimal statistic, but still requires only minutes. 
%Furthermore, the same Bayesian analysis drawn upon by the noise marginalization 
%can be used to compute the optimal statistic with any choice of the ORF, 
%allowing additional spatial correlations to be tested very quickly.
Furthermore, the same Bayesian analysis drawn upon by the noise marginalization 
can be used to compute the optimal statistic for any choice of spatial correlations 
simply by changing the overlap-reduction function (ORF). 
For example, clock errors lead to a common red signal with monopole spatial correlations \citep{hcm+2012}, 
while uncertainty in the SSB produces dipole spatial correlations \citep{chm+2010}. 
This technique is used to perform the frequentist searches 
for common red signals with HD, 
monopole, and dipole spatial correlations 
in the NANOGrav 11-year data set \citep{abb+17b}.

@@

The optimal statistic is constructed from the autocovariance and cross-covariance matrices 
$C_a$ and $S_{ab}$, 
\begin{eqnarray}
	C_a &=& \left\langle \res_a \res_a^T \right\rangle \,, \\
	S_{ab} &=& \left. \left\langle \res_a \res_b^T \right\rangle \right|_{a \neq b} \,,
\end{eqnarray}
where $\res_a$ is a vector of the residuals of the $a$th pulsar in the PTA. 
For the GWB with power spectral density (PSD) $P_\mathrm{gw}(f)$ 
and overlap reduction function (ORF) $\Gamma_{ab}$, 
the cross-covariance matrices are
\begin{equation}
	S_{ab} = F_a \, \phi_{ab}^\mathrm{gw} \, F_b^T \,,
\end{equation}
where
\begin{equation}
	\phi_{ab}^\mathrm{gw} = \Gamma_{ab} \, P_\mathrm{gw}(f) \,.
	\label{eq:phi_gw}
\end{equation}
The ORF is the HD curve \citep{hd1983}, 
\begin{eqnarray}
	\Gamma_{ab} &=& \frac{1}{2} \left[ 1 - \frac{1}{2} \left( \frac{1-\cos\theta_{ab}}{2} \right) \right. \nonumber \\
		&& \left. + 3 \left( \frac{1-\cos\theta_{ab}}{2} \right) \ln \left( \frac{1-\cos\theta_{ab}}{2} \right) \right]  \,,
\end{eqnarray}
where $\theta_{ab}$ is the angle between the pulsars. 
We model the PSD of the GWB as a power law:
\begin{equation}
	P_\mathrm{gw}(f) = \frac{\Agw^2}{12\pi^2} \left( \frac{f}{f_\mathrm{yr}} \right)^{-\gamma} \,,
\end{equation}
where $\gamma = 13/3$ assuming SMBHBs evolve solely due to GW emission and $f_\mathrm{yr} \equiv 1/(1\,\mathrm{yr})$. 
The optimal statistic $\hat{A}^2$ is given by
\begin{equation}
	\hat{A}^2 = \frac{\sum_{ab} \res_a^T {C_a^{-1} \tilde{S}_{ab} C_b^{-1} \res_b}}{\sum_{ab} \Tr \left( C_a^{-1} \tilde{S}_{ab} C_b^{-1} \tilde{S}_{ba} \right) } \,,
\end{equation}
where $\tilde{S}_{ab}$ is the amplitude-independent cross-correlation matrix,
\begin{equation}
	\Agw^2 \tilde{S}_{ab} = S_{ab} \,.
\end{equation}
This definition of the optimal statistic ensures that  
$\langle \hat{A}^2 \rangle = \Agw^2$. 
If $\Agw=0$, the variance of the optimal statistic is
\begin{equation}
	\sigma_0 = \left[ \sum_{ab} \Tr \left( C_a^{-1} \tilde{S}_{ab} C_b^{-1} \tilde{S}_{ba} \right) \right]^{-1/2} \,.
\end{equation}
For a measured value of $\hat{A}^2$, 
the significance of $\hat{A}^2 \neq 0$ is given by the signal-to-noise ratio (SNR) 
\begin{equation}
	\rho = \frac{\sum_{ab} \res_a^T {C_a^{-1} \tilde{S}_{ab} C_b^{-1} \res_b}}{ \left[ \sum_{ab} \Tr \left( C_a^{-1} \tilde{S}_{ab} C_b^{-1} \tilde{S}_{ba} \right) \right]^{1/2}} \,.
\end{equation}

When constructing the residuals $\res_a$, 
we typically fix the red noise parameters to the values that 
maximize the single-pulsar likelihood. 
However, this leads to a bias in the optimal statistic 
because the individual red noise and common red noise parameters 
are highly covariant, 
with the optimal statistic computed using fixed red noise parameters 
systematically lower than the true value of $\Agw^2$. 
In this section, we compare three techniques for computing the optimal statistic. 
First, we fix the individual pulsars' red noise parameters to the 
maximum-likelihood values from individual Bayesian pulsar noise analyses. 
Second, we fix the pulsars' red noise parameters to the 
values that jointly maximize the likelihood for a Bayesian analysis 
of all of the pulsars in our PTA 
that searches over the pulsars' red noise parameters and 
a common red process. 
For the noise-marginalized method, we draw values of the pulsars' 
red noise parameters from the posteriors generated by the common Bayesian analysis.

We use these methods to compute the optimal statistic 
for simulated ``NANOGrav-like'' data sets 
consisting of 18 MSPs with observation times, 
sky positions, and noise properties 
matching the 18 longest-observed pulsars in the 
NANOGrav 11-year data set \citep{abb+17}. 
We include white noise for all pulsars, plus 
red noise parametrized as a power law, 
\begin{equation}
	P_a(f) = \frac{A_\mathrm{red}^2}{12\pi^2} \left( \frac{f}{f_\mathrm{yr}} \right)^{-\gamma} \,,
\end{equation}
for those pulsars that show evidence of red noise 
(see Table~\ref{tab:sim} for more details).
We use the PTA data analysis package 
PAL2 %\footnote{\href{https://github.com/jellis18/PAL2}{https://github.com/jellis18/PAL2}} 
\citep{evh17a}
to perform the noise analyses and compute the optimal statistic.

@@

This overlap between the monopole, dipole, and HD ORFs also means that 
a common red process that does not have HD correlations  
may be confused for a GWB. Figure~\ref{fig:os_dipole} shows the results of 300 simulations 
containing a stochastic signal with dipole spatial correlations. 
Although a dipole signal has been injected, 
the HD ORF gives a mean SNR greater than 5 in 82\% of the simulations. 
However, both the monopole and HD ORFs give smaller values of 
the mean $\hat{A}^2$ and mean SNR compared to the dipole ORF. 
Furthermore, there are no simulations for which the mean SNR with HD ORF 
is greater than the mean SNR with dipole ORF. 
This demonstrates the importance of comparing the SNR from different spatial correlations 
when determining the type of spatial correlations present.
\begin{figure}[t]
	\includegraphics[width=0.9\columnwidth]{plots/optstat_dipole_A5e-15.pdf}
	\caption{Noise-marginalized mean optimal statistic and mean SNR for 300 simulated data sets 
			containing an injected stochastic signal with dipole spatial correlations and $A = 5\times10^{-15}$. 
			We compare the values of the optimal statistic and mean SNR 
			found using monopole (blue), dipole (orange), 
			and HD (green) spatial correlations. 
			The dashed vertical line indicates the injected value, $\hat{A}^2 = 2.5 \times 10^{-29}$.}
	\label{fig:os_dipole}
\end{figure}

@@

The significance of spatial correlations can also be tested with ``sky scrambles,'' 
where the ORF is altered in order to simulate changing the pulsars' positions \citep{cs2016,tlb+2017}. 
The scrambled ORFs are required to have small values of $\bar{M}$ 
with the true ORF and each other so that they form a nearly-orthogonal set. 
This ensures that the distribution of $\hat{A}^2$ computed using the scrambled ORFs 
forms the null hypothesis distribution. 
\citet{tlb+2017} showed how sky scrambles affect the Bayes' factor for simulated data sets. 
We performed a similar analysis using frequentist methods.

@@

\acknowledgments
We thank Joe Lazio, Andrea Lommen, Joe Romano, Xavier Siemens, 
and Jolien Creighton for useful discussions. 
This work was supported by NSF Physics Frontier Center Grant 1430284. 
%SRT was partially supported by appointment to the NASA Postdoctoral Program 
%at the Jet Propulsion Laboratory, which is administered by Oak Ridge Associated Universities 
%and the Universities Space Research Association through a contract with NASA. 
JAE was partially supported by NASA through Einstein Fellowship Grant PF4-150120. 
We are grateful for computational resources provided by the Leonard E Parker
Center for Gravitation, Cosmology and Astrophysics at the University of
Wisconsin-Milwaukee supported by NSF Grant 0923409.
